pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-03-18 article.tex
Merge introduction of ERQ 3

In ERQ 1 we measured the baseline error of the \verb;pirouette; method, 
by using a standard tree prior in both the generation of the tree 
and in our inference.
The goal of \verb;pirouette; is to quantify the 
influence of a new (non-standard) tree prior.
To do so, we need to compare the inference error 
from the new tree prior to a baseline error,
by use of a twin tree (see subsection~\ref{subsec:twinning}).
In this ERQ, we assume the new tree prior so closely related to
a standard tree prior, that we hand-pick a standard tree prior to
serve as a stand-in generative tree prior.

@@

In ERQ 1 we built the twin pipeline. At the end of the section we discussed how it has not much relevance if considered as a stand-alone process. Here, instead, we will use it as a control for the main pipeline, where the generative tree prior $\mathit{P}$ is unknown, but the site and clock models used for the inference are the ones used to simulate the alignment.
This leads to the third ERQ:

>>>>

In ERQ 1 we measured the baseline error of the \verb;pirouette; method, 
by using a standard tree prior in both the generation of the tree 
and in our inference.
The goal of \verb;pirouette; is to quantify the 
influence of a new (non-standard) tree prior.
To do so, we need to compare the inference error 
from the new tree prior to a baseline error,
by use of a twin tree (see subsection~\ref{subsec:twinning}).
To do so, we use the twin tree as a control for the main pipeline.
In this example, we do not know the generative tree prior $\mathit{P}$,
but we do know the alignment model, $\mathit{A}$.
In this ERQ, we assume the new tree prior is so closely related to
a standard tree prior, that it is reasonable to hand-pick a standard tree prior 
to serve as a stand-in generative tree prior.

@@
